Investing in infants: the lasting effects of cash transfers to new families

### 2024-07-31 posts/BarrEgglestonSmith/BarrEgglestonSmith2022.qmd
Added research question page to BarrEgglestonSmith2022.html

@@

::: {.incremental}
* $\sigma$&uarr; = $2500&uarr; at age 28 per year [@ChettyFriedmanRockoff2014b]  
* .037$\sigma$ (per \$1000)$\times$ $2500=$92 per year per $1000 spent  
   * 9.2% is pretty high...   
* "(C)ould entirely account for our observed wage effects ... $353 per $1000" (?)  
:::

>>>>

## Research question

::: {.incremental}
* Does providing cash at infancy (< 1 year) have a long run impact on welfare?  
* Use fiscal year cutoff for EITC. Born on:  
   * Dec 31 receives after +1 day  
   * Jan 1 receives after +1 year  
* Examine with tax records + social security numident file (birth day)  
:::

@@

::: {.incremental}
* Exam score $\sigma$&uarr; \Rarr; $2500&uarr; at age 28 per year [@ChettyFriedmanRockoff2014b]  
* .037$\sigma$ (per \$1000)$\times$ $2500=$92 per year per $1000 spent  
   * 9.2% is pretty high...   
* "(C)ould entirely account for our observed wage effects ... $353 per $1000" (?)  
:::
